Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2006-07-04 paper/space.tex
slight corrections

\begin{definition}[Maximum Path Length, Suffix Depth]
$l$ is the string depth of the deepest branching node in the tree.
%
%\[ l = \max_{\overline{w} \in \mathcal{T}} |w| \mbox{ and $\overline{w}$ isn't a leaf} \]
%\end{definition}

%\begin{definition}[Suffix-Depth]
For any node $\overline{w}$ its suffix-depth is the number of nodes which must be followed to reach the root, which is $|w|$. It is obvious that $l$ is a maximum on the suffix-depth of nodes.
\end{definition}

>>>>

\begin{definition}[Maximum Path Length, Suffix Depth]
Let $l$ be the string depth of the deepest branching node in the tree~\footnote{For a node \Node, its string depth is $|w|$.}.

For any node $\overline{w}$ its suffix-depth is the number of nodes which must be followed to reach the root, which is $|w|$. It is obvious that $l$ is a maximum on the suffix-depth of nodes.
\end{definition}

### 2006-07-04 paper/structure.tex
slight corrections

\begin{definition}[Patricia tree]
$T$ is a Patricia tree if $T$ is a rooted tree with edge labels from $\Sigma^+$. For each $a \in \Sigma$ and every node $n$ in $T$, there is at most one edge leaving $n$ whose label starts with $a$. Each node in a Patricia tree has a path leading to it which forms a string. If the node $n$ has the leading path $w$, we shall also refer to $n$ as $\overline{w}$.
\end{definition}

@@

\begin{definition}[Suffix Tree, Suffix Link]
A \emph{suffix tree} for a string $S$ is a Patricia tree whose leaf nodes (those without children) have paths corresponding to all suffixes of the string $S\$ $. A suffix link in a suffix tree is a link from the node $\overline{aw}$ to the node $\overline{w}$. This link has the label $a$.
\end{definition}

@@

Suffix trees are normally implemented by associating with each node two indices into the original string which are the start and end position of its incoming edge.

>>>>

\begin{definition}[Patricia tree]
$T$ is a Patricia tree if $T$ is a rooted tree with edge labels from $\Sigma^+$. For each $a \in \Sigma$ and every node $n$ in $T$, there is at most one edge leaving $n$ whose label starts with $a$. Each node in a Patricia tree has a path leading to it which forms a string. If the node $n$ has the leading path $w$, we shall also refer to $n$ as $\overline{w}$.

A \emph{compact} Patricia tree is one with no nodes with just one child.
\end{definition}

@@

\begin{definition}[Suffix Tree, Suffix Link]
A \emph{suffix tree} for a string $S$ is a compact Patricia tree whose leaf nodes (those without children) have paths corresponding to all suffixes of the string $S\$ $. A suffix link in a suffix tree is a link from the node $\overline{aw}$ to the node $\overline{w}$. This link has the label $a$.
\end{definition}

@@

Suffix trees are normally implemented by associating with each node two indices into the original string which are the start and end position of its incoming edge. This allows the structure to be kept in $\bigO(n)$ space.
